Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-07-17 lqg-strings.tex
Completed my part of discussion

Our goal is to write down the action of a string propagating in a background geometry. One might argue that the expression \eqref{eqn:polyakov-gravity}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet already describes the string in an arbitrary background geometry. However, we view this approach as unsatisfactory, not the least because it does not allow us to make contact of the string action with a background geometry specified in terms of connection variables instead of metric ones. An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \eqref{eqn:polyakov-gravity} with $E_\mu^I E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat coordinates). This, however, leaves open the question of what role the bulk connection should play in this picture.

@@

Assuming that $l_{pl} \ll l_s$, we have $k \ll 1$ and consequently \eqref{eqn:ng-area-corrected} can be expanded as a power series in $k$. Keeping only the term linear in $k$, we obtain an action which is the sum of two copies of the Nambu-Goto action, one for the original metric $h_{ab}$ and the second for the inverse metric $h^{ab}$. We then pointed out the similarity between this expression and previous studies of \emph{bimetric gravity} \cite{Hassan2012Bimetric}. We also want to point that though the possible relationship between string theory and bimetric gravity has been investigated before by \cite{Lust2021Extracting,Yan2021Strings}, these authors have looked at bimetric gravity in the \emph{bulk} geometry rather than a bimetric action for the worldshee, itself, of the type given in \eqref{eqn:modified-ng-action-v2}.

@@

\textbf{Steps which led us here}

\begin{itemize}
	\item We seek to describe the behavior of a string in an arbitrarily curved background geometry.
	\item Connection variables are used in LQG to describe geometry. So we should search for non-metrical description of coupling string geometry to bulk.
	\item For arbitrarily curved bulk geometry, global Poincare symmetry of embedding fields is meaningless.
	\item Elevate global Poincare to local Poincare following the lessons of gauge theory, which leads to introduction of extra "holographic" co-ordinate.
	\item Investigate physical implications of holographic co-ordinate for string phenomenology in this picture.
\end{itemize}

@@

The obvious drawback of this approach is that the background metric is non-dynamical and is fixed to be the flat Minkowski metric $\eta_{\mu\nu}$. Clearly, one would like to be able to understand the physics of a string propagating on an arbitrary curved background. It wouldn't make much sense to refer to string theory as a theory of ``quantum gravity'' if strings can only be described on flat backgrounds. The way this is accomplished is by treating the metric of the worldvolume as a ``background field'' $G_{\mu\nu}$, in terms of which the Polyakov action becomes:
\begin{equation}\label{eqn:polyakov-gravity}
	S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
\end{equation}
where the bulk metric is now a function of the bulk coordinates $G_{\mu\nu}(X)$. Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-gravity} does not contain any terms with time derivatives of $G_{\mu\nu}$. However, if we view the action purely as a two-dimensional theory of $D$ scalar fields, then the bulk metric can be viewed as a collection of \emph{coupling constants}, rather than a dynamical entity which exists independent of the string. One can now proceed in the usual manner for any field theory and calculate the beta function of the coupling constants of the theory as a function of the energy scale.

>>>>

Our goal is to write down the action of a string propagating in a background geometry. One might argue that the expression \eqref{eqn:polyakov-curved-bulk}, where we replace the bulk Minkowski tensor $\eta_{\mu\nu}$ with an arbitrary tensor $G_{\mu\nu}$ which tells us what the components of the bulk metric are at that point on the worldsheet already describes the string in an arbitrary background geometry. However, we view this approach as unsatisfactory, not the least because it does not allow us to make contact of the string action with a background geometry specified in terms of connection variables instead of metric ones. An astute reader might correctly object saying that we can simply replace $G_{\mu\nu}$ in \eqref{eqn:polyakov-curved-bulk} with $E_\mu^I E_\nu^J \eta_{IJ}$ (here $\eta_{IJ}$ is now the Minkowski metric in locally flat coordinates). This, however, leaves open the question of what role the bulk connection should play in this picture.

@@

Assuming that $l_{pl} \ll l_s$, we have $k \ll 1$ and consequently \eqref{eqn:ng-area-corrected} can be expanded as a power series in $k$. Keeping only the term linear in $k$, we obtain an action which is the sum of two copies of the Nambu-Goto action, one for the original metric $h_{ab}$ and the second for the inverse metric $h^{ab}$. We then pointed out the similarity between this expression and previous studies of \emph{bimetric gravity} \cite{Hassan2012Bimetric}. We also want to point that though the possible relationship between string theory and bimetric gravity has been investigated before by \cite{Lust2021Extracting,Yan2021Strings}, these authors have looked at bimetric gravity in the \emph{bulk} geometry rather than a bimetric action for the worldsheet, itself, of the type given in \eqref{eqn:modified-ng-action-v2}.

@@

After exploring the equations of motion ... \textbf{Luigi ... fill in summary of your work here on solving eoms and on emergent dimensions}

Ultimately one cannot be satisfied with the heuristic action of the form \eqref{eqn:ng-area-corrected}. Therefore in \autoref{sec:holographic-strings} we attempt to build, from the ground up, a modified string action which incorporates the following chain of thought. We seek to describe the behavior of a string in an arbitrarily curved background geometry at a \emph{classical} level. For this an action of the form \eqref{eqn:polyakov-curved} is unsuitable because that action treats the bulk metric as non-dynamical variables. Connection variables are used in LQG to describe the geometry of a manifold. The coupling of the string worldsheet to the bulk geometry should reflect this fact. This leads us to an action of the form \eqref{eqn:poincare-polyakov}. This action no longer possess the global Poincaré symmetry of the original Polyakov action. However it is invariant under \emph{local} Poincaré gauge transformations.

For an arbitrarily (or even a minor deviation from flat space) curved bulk geometry, global Poincaré symmetry of embedding fields is not meaningful. Local Poincaré symmetry, on the other hand, provides a perfectly adequate framework \cite{Hehl2023Four} for constructing a theory of gravity on an arbitrary bulk. Thus we conjecture that the bulk theory is that of gauged Poincaré gravity.

Finally, the interpretation of embedding fields as co-ordinate fields on the bulk and \emph{also} as vectors living in the fundamental representation of the Poincaré group necessitates the introduction of an ``auxiliary'' co-ordinate which has the natural interpretation as a holographic or scale direction.

@@

The obvious drawback of this approach is that the background metric is non-dynamical and is fixed to be the flat Minkowski metric $\eta_{\mu\nu}$. Clearly, one would like to be able to understand the physics of a string propagating on an arbitrary curved background. It wouldn't make much sense to refer to string theory as a theory of ``quantum gravity'' if strings can only be described on flat backgrounds. The way this is accomplished is by treating the metric of the worldvolume as a ``background field'' $G_{\mu\nu}$, in terms of which the Polyakov action becomes:
\begin{equation}\label{eqn:polyakov-curved-bulk}
	S'_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu G_{\mu\nu}(X),
\end{equation}
where the bulk metric is now a function of the bulk coordinates $G_{\mu\nu}(X)$. Now this metric is still non-dynamical because the action \eqref{eqn:polyakov-curved-bulk} does not contain any terms with time derivatives of $G_{\mu\nu}$. However, if we view the action purely as a two-dimensional theory of $D$ scalar fields, then the bulk metric can be viewed as a collection of \emph{coupling constants}, rather than a dynamical entity which exists independent of the string. One can now proceed in the usual manner for any field theory and calculate the beta function of the coupling constants of the theory as a function of the energy scale.
